Are we living in a depressive society?

### 2024-04-02 outputs/paper/paper.qmd
Add introduction and abstract. Modify the references.bib file

---
title: "Are we living in a depressive society?"
subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"
author: Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder."
date: today
date-format: long
abstract: "Analyzing data spanning from 2020 to 2024, we examine variatinos in anxiety or depressive disorders among different age groups, sex, race/ethnicity, and education level. Our analysis yncovers additional factors contributing to this trend. "
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Depression and anxiety are common symptoms of mental disorders in modern world. It could be light or serious. Someone could suffer it for longer period of time than the others, or someone could go through on a regular basis. It could be due to hormonal effect or circumstance that one confronting or even a weather can affect such level. !!According to ~ depression is ~ anxiety ~ !! It is not a country specific problem, but matters in the whole generation in global scale.

Due to the Covid-19 global pandemic, many countries took a lockdown measure and the US was not the exceptional. The U.S. Census Bureau launched the Household Pulse Survey to produce data on the social and economic impacts of Covid-19 on American households in collaboration with five federal agencies. The Household Pulse Survey was designed to gauge the impact of the pandemic on employment status, consumer spending, food security, housing, education disruptions, and dimensions of physical and mental wellness (NCHS, 2024). Here the dataset is about the estimate of anxiety or depression under the mental wellness category.

The estimand is the difference in whether a rate of symptoms of anxiety or depressive disorder of an individual would be correlated with the socio-cultural factors including age, sex, race/ethnicity, and education.

This paper utilizes R (R Core Team 2020) for analysis, leveraging packages such as ggplot2(Wickham et al. 2016) for creating graphical representations. Additionally, the gridExtra package was used to enhance the layout and presentation of the figures (Murrell 2021) !!+ add more packages that was used in the paper. !!

The structure of the paper is following, data is

>>>>

---
title: "Are we living in a depressive society?"
subtitle: "Trends in symptoms of anxiety or depressive disorder in the US population from May 2020 to March 2024"
author: Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder."
date: today
date-format: long
abstract: "This study explores how socio-cultural factors like age, sex, race/ethnicity, and education level influenced anxiety and depressive disorders in the U.S. during and after the COVID-19 pandemic, analyzing data from 2020 to 2024. Using advanced statistical methods in R, it uncovered significant variations in mental health impacts across different demographic groups. The research reveals a complex relationship between socio-cultural factors and mental health, highlighting the increased vulnerability of certain populations during global crises. These insights are crucial for developing targeted public health strategies to mitigate mental health issues during and after pandemics, enhancing our understanding of how socio-cultural dynamics shape mental wellness in times of crisis."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

Depression and anxiety are not only prevalent but escalating issues in the modern world, affecting individuals across the globe regardless of demographic factors (World Health Organization, 2021). These mental health challenges have been further exacerbated by the COVID-19 pandemic, which led to widespread social and economic upheaval (Brooks et al., 2020). While various studies have explored the impact of the pandemic on mental health, there remains a significant gap in understanding the nuanced interactions between socio-cultural factors and the prevalence of anxiety and depressive disorders during this period (Pfefferbaum & North, 2020).

This paper addresses this gap by analyzing data from the U.S. Census Bureau's Household Pulse Survey, initiated in response to the pandemic to assess its effects on American households, including mental wellness (U.S. Census Bureau, 2020). Our analysis focuses on the correlation between the prevalence of anxiety or depressive disorders and socio-cultural factors such as age, sex, race/ethnicity, and education level during the pandemic and post pandemic years of 2020 to 2024. Specifically, the estimand of this study is the difference in the rates of symptoms of anxiety or depressive disorders across individuals, correlated with socio-cultural factors including age, sex, race/ethnicity, and education level.

Employing a quantitative methodology, this paper utilizes R (R Core Team 2020) for analysis. We utilized packages like ggplot2 (Wickham et al., 2016) and gridExtra (Murrell, 2021) for data analysis and visualization. Our findings reveal significant trends and disparities in the rates of anxiety and depressive disorders across different socio-cultural groups, highlighting the intricate relationship between these factors and mental health outcomes during the pandemic.

The importance of this research lies in its potential to inform public health policies and interventions, aiming to mitigate the adverse effects of such global crises on mental health (Xiong et al., 2020). By understanding the specific socio-cultural factors that contribute to increased vulnerability to anxiety and depressive disorders, targeted strategies can be developed to support affected populations more effectively.

The paper is structured to first present the trend analysis of anxiety and depressive disorder rates in the U.S. from 2020 to 2024, followed by an examination of how these rates vary across different demographic groups. Subsequent sections delve into the statistical methods and results for each research question, culminating in a discussion that synthesizes the findings and explores their broader implications for mental health research and policy. The conclusion summarizes the key insights, acknowledges the limitations of the study, and suggests avenues for future research.

The study focuses on answering the following research questions:

* What is the trend in US anxiety and depressive disorder rates from 2020 to 2024?

* How do anxiety and depressive rates vary across different age groups?

* How do anxiety and depressive rates differ based on race and ethnicity?

* How do anxiety and depressive rates differ based on sex?

* How do anxiety and depressive rates differ based on education level?
